Estimating the Initial Susceptible Fraction in Dengue Dynamics

### 2014-11-20 draft_lm1.tex
organising the plots --  draft
removing redundant term

Many authors have derived $c_{\alpha}(\theta_t)$ following orthodox approaches 
such as those of \cite{wilson} and \cite{clopper}, mainly for simplicity 
reasons.
We choose instead to take a Bayesian approach and use the  $100\alpha \%$ 
posterior credibility interval for $\theta_t$ as $c_{\alpha}(\theta_t)$.
If we choose the conjugate beta prior with parameters $a_0$ and $b_0$ for the 
binomial likelihood in (\ref{eq:binlike}), the posterior distribution for 
$\theta_t$ is
\begin{equation}
\label{eq:thetapost}
p(\theta_t| Y_{t+1}, S) \sim Beta(Y_{t+1} + a_0, Y_t + b_0)
\end{equation}
Equation~(\ref{eq:thetapost}) tells us that the induced distribution of $R_t$ is 
a beta prime with parameters $ a_1 = Y_{t+1} + a_0$ and $b_1 =  Y_t + b_0$.
The density of this induced distribution  $f_P(R_t)$ is then 
\begin{equation}
\label{eq:densityMantel}
f_P(R_t| a_1, b_1) = \frac{\Gamma(a_1 + b_1)}{\Gamma(a_1)\Gamma(b_1)} R_t^{a_1 - 
1} (1 + R_t)^{-(a_1 + b_1)}
\end{equation}
Thus, the expectation of \rr under $f_P$ is $a_1/(b_1 - 1)$ and its variance is 
$a_1(a_1 + b_1 - 1)/\left((b_1 - 2)(b_1 - 1)^2 \right) $.

@@

\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}
\begin{center}
\includegraphics[width=.9\textwidth]{./concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. 
Scatter plot shows the observed cases. Prevalences are scaled as fractions 
of the entire population.
}
\label{Fig:S0}
\end{figure}

>>>>

Many authors have derived $c_{\alpha}(\theta_t)$ following orthodox approaches 
such as those of \cite{wilson} and \cite{clopper}, mainly for simplicity.
We choose instead to take a Bayesian approach and use the  $100\alpha \%$ 
posterior credibility interval for $\theta_t$ as $c_{\alpha}(\theta_t)$.
If we choose the conjugate beta prior with parameters $a_0$ and $b_0$ for the 
binomial likelihood in (\ref{eq:binlike}), the posterior distribution for 
$\theta_t$ is
\begin{equation}
\label{eq:thetapost}
p(\theta_t| Y_{t+1}, S) \sim Beta(Y_{t+1} + a_0, Y_t + b_0)
\end{equation}
Equation~(\ref{eq:thetapost}) tells us that the induced distribution of $R_t$ is 
a beta prime with parameters $ a_1 = Y_{t+1} + a_0$ and $b_1 =  Y_t + b_0$.
The density of this induced distribution  $f_P(R_t)$ is then 
\begin{equation}
\label{eq:densityMantel}
f_P(R_t| a_1, b_1) = \frac{\Gamma(a_1 + b_1)}{\Gamma(a_1)\Gamma(b_1)} R_t^{a_1 - 
1} (1 + R_t)^{-(a_1 + b_1)}
\end{equation}
Thus, the expectation of \rr under $f_P$ is $a_1/(b_1 - 1)$ and its variance is 
$a_1(a_1 + b_1 - 1)/\left((b_1 - 2)(b_1 - 1)^2 \right) $.

@@

\bibliography{lm1}
\section*{Figure Legends}
% This section is for figure legends only, do not include
% graphics in your manuscript file.
%
%\begin{figure}
%\caption{
%{\bf Bold the first sentence.}  Rest of figure caption.  
%}
%\label{Figure_label}
%\end{figure}
\begin{figure}
\begin{center}
\includegraphics[width=.9\textwidth]{plots/concat_SI.png}
\end{center}
\caption{
{\bf Susceptibles and Infectious posterior curves.}  The curves were estimated 
only for the periods where $R_t> 1$.  The susceptible curves in the top panel 
reflect the prevalence of fraction of susceptibles to circulating strain(s) for 
each epidemic/outbreak. In the lower panel see the posterior distribution 
of infectious curves, represented by its Median and 95\% credible interval. 
Scatter plot shows the observed cases. Prevalences are scaled as fractions 
of the entire population.
}
\label{Fig:S0}
\end{figure}
